Manuscript Draft\\ \vspace{2cm} What is long-distance dispersal? And a taxonomy of dispersal events \\ \textbf{Supplementary Material}

### 2016-06-28 Manuscript/MS- What is LDD.tex
Minor edits to SupplMat and figure legends.

\textbf{Figure 2}. Schematic representation of different types of long-distance dispersal events in relation to the geographical limits of local populations (dashed lines) and the genetic neighborhood area $N_b$ (grey area) of specific individual plants (squares). Dispersal events (arrows) can be classified depending on their actual incidence on propagule movement outside these spatially-explicit reference areas (Table 1). Strict-sense long-distance dispersal events ($LDD_{ss}$) just include the LDD events that disseminate propagules out of \textit{both} the population and genetic neighborhood boundaries. A, the neighborhood area is included within the geographic limits of the population; B, the neighborhood area is much larger than the geographic limits of the population.\\

\textbf{Figure 3}. Empirical frequency distributions of seed dispersal events as a function of dispersal distance by animal frugivores consuming \textit{Prunus mahaleb} fruits. In red, left (inset), frequencies of within-populations dispersal events inferred from direct assignment based on seed endocarp genotypes and maternal trees genotypes. Larger frame, left, contributions of four functional frugivore groups (small birds, medium- and large-sized birds, and mammals) to seed dissemination and proportional contributions (right bar) to dispersal of the inferred immigrant seeds (i.e., those not matching any maternal tree in the study population).\\

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the four combinations of \textit{Prunus mahaleb} seed dispersal events outlined in Table 1. These result from dissemination within (yellow) or outside (blue) the population geographic limits ($SDD_{loc}$, $LDD_{loc}$, respectively) and within or outside the genetic neigborhood area limits ($SDD_{neigh}$, $LDD_{ss}$, respectively).\\ 
\newpage

>>>>

\textbf{Figure 2}. Schematic representation of different types of long-distance dispersal events in relation to the geographical limits of local populations (dashed lines) and the genetic neighborhood area $N^b_e$ (grey area) of specific individual plants (squares). Dispersal events (arrows) can be classified depending on their actual incidence on propagule movement outside these spatially-explicit reference areas (Table 1). Strict-sense long-distance dispersal events ($LDD_{ss}$) just include the LDD events that disseminate propagules out of \textit{both} the population and genetic neighborhood boundaries. A, the neighborhood area is included within the geographic limits of the population, with some dispersal events potentially contributing local LDD; B, the neighborhood area is much larger than the geographic limits of the population.\\

\textbf{Figure 3}. Empirical frequency distributions of seed dispersal events as a function of dispersal distance by animal frugivores consuming \textit{Prunus mahaleb} fruits. In red, left (inset), frequencies of within-population dispersal events inferred from direct assignment based on seed endocarp genotypes and maternal trees genotypes. Larger frame, left, contributions of four functional frugivore groups (small birds, medium- and large-sized birds, and mammals) to seed dissemination and proportional contributions (right bar) to dispersal of the inferred immigrant seeds (i.e., those not matching any maternal tree in the study population) \citep{Jordano:2007}.\\

\textbf{Figure 4}. Differential contributions of functional groups of frugivores to the four combinations of \textit{Prunus mahaleb} seed dispersal events outlined in Table 1. These result from dissemination within (yellow) or outside (blue) the population geographic limits; within-population dispersal events can either be short-distance ($SDD_{loc}$) or local LDD ($LDD_{loc}$) depending on the size of the genetic neigborhood. Dispersal outside the local population can entail short-distance dispersal, if within the genetic neighborhood area limits ($SDD_{neigh}$) (yellow) or represent strict-sense LDD ($LDD_{ss}$) (blue).\\ 
\newpage

### 2016-06-28 Manuscript/SupplMat.tex
Minor edits to SupplMat and figure legends.

\paragraph*{Species and Study Site.} The study species, \textit{Prunus mahaleb} (L.) (Rosaceae), is a shrub or small tree that produces fleshy fruits that are consumed by frugivores, who disperse seeds after regurgitating or defecating them. This species is frequently visited during July to mid-August by small- and medium-sized birds and carnivorous mammals that include fruits in their diets during late summer to winter \citep{Jordano:2000ft}. \textit{P. mahaleb} occurs in a patchy distribution at the regional scale, with relatively isolated populations consisting of dozens to hundreds of trees. Our study population included a total of 196 adult reproductive trees distributed over an area of 26 ha in patches of variable density. Other populations within 20 km exist as scattered patches of 10–150 trees, with some containing $\geqq$ 1,000 trees. The nearest population is 1.5 km away. Additional information on the study population is reported by \citet{Jordano:2007} and \citet{Garcia:2009do}.

@@

In addition we sampled directly the pellets of large corvids (\textit{Corvus corone}) and from \textit{Turdus viscivorus}, the latter by direct sampling beneath pine trees and scats from seed traps \citep[see ][ for details]{Jordano:2007}. Finally, a seed sample directly from seed traps included seeds dispersed by small- and medium-sized passerines, such as \textit{Phoenicurus ochruros}, \textit{Turdus merula}, \textit{Erithacus rubecula}, \textit{Sylvia communis}, \textit{Sylvia atricapilla}, etc. \citep{Jordano:2007}. The total seed sample thus consisted of seed endocarps collected from the seed traps (mostly small passerines) ($n= $465), mammal scats ($n= $167), and \textit{C. corone} pellets ($n= $23).

@@

Once the maternal source tree of each individual seed was identified (or its provenance from outside the study population determined) we assessed the dispersal distance and grouped the seeds separately as coming from trees locate within or outside the population. In addition, for seeds originating from local trees we determined whether dispersal distances were $\geqq$ 45 m to sort out $LDD_{loc}$ dispersal events from $SDD_{loc}$ events. All the events involving immigrant seeds were considered $LDD_{ss}$ by definition, given that the neighborhood size was very reduced (radius= 0.045 km) relative to the geographic limits of the study population (maximum length for a within-population dispersal event: 1220 m)\citep{Garcia:2009do}. Along this reasoning, $LDD_{neigh}$ events were considered non-existent in this particular case study given that neighborhood size area was smaller than the population area.

>>>>

\paragraph*{Species and Study Site.} The tree species we use as a case study to illustrate different types of dispersal events, \textit{Prunus mahaleb} (L.) (Rosaceae), is a shrub or small tree that produces fleshy fruits that are consumed by frugivores, who disperse seeds after regurgitating or defecating them. This species is frequently visited during July to mid-August by small- and medium-sized birds and carnivorous mammals that include fruits in their diets during late summer to winter \citep{Jordano:2000ft}. \textit{P. mahaleb} occurs in a patchy distribution at the regional scale, with relatively isolated populations consisting of dozens to hundreds of trees. Our study population included a total of 196 adult reproductive trees distributed over an area of 26 ha in patches of variable density. Other populations within 20 km exist as scattered patches of 10–150 trees, with some containing $\geqq$ 1,000 trees. The nearest population is 1.5 km away. Additional information on the study population and description of methodological apporaches is reported by \citet{Jordano:2007} and \citet{Garcia:2009do} and references therein.

@@

In addition we sampled directly the pellets of large corvids (\textit{Corvus corone}) and from \textit{Turdus viscivorus}, the latter by direct sampling beneath pine trees and scats from seed traps \citep[see ][ for details]{Jordano:2007}. Finally, a seed sample directly from seed traps included seeds dispersed by small- and medium-sized passerines, such as \textit{Phoenicurus ochruros}, \textit{Turdus merula}, \textit{Erithacus rubecula}, \textit{Sylvia communis}, \textit{Sylvia atricapilla}, etc. \citep{Jordano:2007}. The total seed sample thus consisted of seed endocarps collected from the seed traps (mostly small passerines) ($n= $465), mammal scats ($n= $167), and \textit{C. corone} pellets ($n= $23) \citep[see Table 1 in ][]{Jordano:2007}.

@@

Once the maternal source tree of each individual seed was identified (or its provenance from outside the study population determined) we assessed the dispersal distance and grouped the seeds separately as coming from trees located within or outside the population. In addition, for seeds originating from local trees we determined whether dispersal distances were $\geqq$ 45 m to sort out $LDD_{loc}$ dispersal events from $SDD_{loc}$ events. All the events involving immigrant seeds were considered $LDD_{ss}$ by definition, given that the neighborhood size was very reduced (radius= 0.045 km) relative to the geographic limits of the study population (maximum length for a within-population dispersal event: 1220 m)\citep{Garcia:2009do}. Along this reasoning, $LDD_{neigh}$ events were considered non-existent in this particular case study given that neighborhood size area was smaller than the population area.
